Questioning how Researchers Develop and Present Intrusion Detection Systems

### 2014-09-19 docs/questioning.tex
added a csrf entry
completed citations

	&  	{\sc csse}~\cite{PB05} & 0 & \xmark,\xmark & 2--10\% & {\sc sql} \\

@@

@@

    &  	{\it {\sc wasc}}~\cite{NLC07} & 0 & \xmark,\xmark & 30\% & {\sc sql}, {\sc xss} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 0 & \xmark,\xmark & 2.2$\times$ & {\sc sql}, {\sc xss}, {\sc php} \\

@@

	&   {\it Noxes}~\cite{KJKV09} & 40 & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\

@@

	\multirow{11}{*}{Policy Enforcement}

@@

	&  {\it {\sc csp}} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\ 

@@

    % &  {\it Phung et al.}~\cite{PSC09} & 75 & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\

@@

@@

	& 	{\it {\sc sd}river}~\cite{MS09,MKS09} & 20 & \tick,\tick & 39\% & {\sc sql}, {\sc xp}ath \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 40 & \xmark,\xmark  & \xmark & {\sc sql}, {\sc xp}ath \\

>>>>

@@

	&  	{\sc csse}~\cite{PB05} & 312 & \xmark,\xmark & 2--10\% & {\sc sql} \\

@@

    &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & \xmark,\xmark & 30\% & {\sc sql}, {\sc xss} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & \xmark,\xmark & 2.2$\times$ & {\sc sql}, {\sc xss}, {\sc php} \\

@@

	&   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\

@@

	\multirow{13}{*}{Policy Enforcement}

@@

	% &  {\it {\sc csp}} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\ 

@@

     &  {\it Phung et al.}~\cite{PSC09} & 75 & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\

@@

    & {\it {\sc soma}}~\cite{OWVS08} & 46 & 5,0,0,0 & 5.58\% & {\sc xss}, {\sc csrf}\\
    & {\it j{\sc csrf}}~\cite{PS11} & 2 & 2,7,0,0 & 2ms & {\sc csrf} \\

@@

	& 	{\it {\sc sd}river}~\cite{MS09,MKS09} & 20,5 & \tick,\tick & 39\% & {\sc sql}, {\sc xp}ath \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql}, {\sc xp}ath \\
